% AUTOGENERATED
\xdtbeforeclasses
\begin{longtabu} to \textwidth { l | X }
\hiderowcolors \multicolumn{2}{l}{\xdtClasses} \tabularnewline \midrule \showrowcolors
Doc\-Walker & A base class for all documentation generators. \\
Program & The command line interface. \\
Tex\-Table\-Walker & A documentation generator that makes separate \LaTeX{} tables for each class
     and a class description table. \\
\bottomrule
\end{longtabu}
\xdtbeforemembers

\xdtbeforemembersof{DocWalker}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Class & public abstract & void & (Class\-Declaration\-Syntax klass, Documentation\-Comment\-Trivia\-Syntax doc) & The callback that gets executed whenever a documentation comment is on a class. \\
On\-Field & public abstract & void & (Field\-Declaration\-Syntax field, Documentation\-Comment\-Trivia\-Syntax doc) & The callback that gets executed whenever a documentation comment is on a field. \\
On\-Property & public abstract & void & (Property\-Declaration\-Syntax property, Documentation\-Comment\-Trivia\-Syntax doc) & The callback that gets executed whenever a documentation comment is on a property. \\
On\-Method & public abstract & void & (Method\-Declaration\-Syntax method, Documentation\-Comment\-Trivia\-Syntax doc) & The callback that gets executed whenever a documentation comment is on a method. \\
Visit\-Trivia & public override & void & (Syntax\-Trivia trivia) & The visitor that executes the callbacks. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Program}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{l}{\textbf{\xdtDescription}} \\
sb & static & String\-Builder & \multicolumn{2}{l}{ The builder of the output string. } \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Header & static & void & (int n, string s) & Outputs a \LaTeX{} header \\
Main & static & void & (string[] args) & The main method. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TexTableWalker}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Member\-Tables & public & Dictionary<string, Class\-Members> & \{ get; \} & The generated member tables in \LaTeX{} syntax. \\
Class\-Table & public & string & \{ get; \} & The generated class table in \LaTeX{} syntax. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Class & public override & void & (Class\-Declaration\-Syntax klass, Documentation\-Comment\-Trivia\-Syntax doc) & Adds a class description to the class table. \\
On\-Field & public override & void & (Field\-Declaration\-Syntax field, Documentation\-Comment\-Trivia\-Syntax doc) & Adds a field description to the member table of its class. \\
On\-Property & public override & void & (Property\-Declaration\-Syntax property, Documentation\-Comment\-Trivia\-Syntax doc) & Adds a property description to the member table of its class. \\
On\-Method & public override & void & (Method\-Declaration\-Syntax method, Documentation\-Comment\-Trivia\-Syntax doc) & Adds a method description to the member table of its class. \\
Esc & private static & string & (string s) & Escapes a string for safe inclusion in a \LaTeX{} table. \\
Class\-Key & private static & string & (Syntax\-Node syntax) & Finds the class name of a given member. \\
\bottomrule
\end{longtabu}
% /MEMBERS
% /AUTOGENERATED
